### 2022-10-14 manuscript.Rmd
Fix tiny bugs

  # Process EEG data
  res <- pipeline$group_pipeline(
    vhdr_files = vhdr_files,
    log_files = logs,
    output_dir = output_dir,
    epochs_dir = here(output_dir, "epochs"),
    report_dir = report_dir,
    downsample_sfreq = 125.0,
    bad_channels = NULL,
    ica_method = "fastica",
    ica_n_components = 0.99,
    highpass_freq = 0.1,
    lowpass_freq = 30.0,
    triggers = c(221, 222),
    epochs_tmin = -0.5,
    epochs_tmax = 1.5,
    baseline = c(-0.2, 0.0),
    reject_peak_to_peak = 150.0,
    components = list(
      "name" = list("P1", "N170", "N400"),
      "tmin" = list(0.1, 0.15, 0.4),
      "tmax" = list(0.15, 0.2, 0.7),
      "roi" = list(
        c("PO3", "PO4", "POz", "O1", "O2", "Oz"),
        c("P7", "P8", "PO7", "PO8", "PO9", "PO10"),
        c("C1", "C2", "Cz", "CP1", "CP2", "CPz")
      )
    ),
    average_by = c("phase/condition"),
    perform_tfr = TRUE,
    tfr_subtract_evoked = FALSE,
    tfr_freqs = seq(4, 40, by = 1.0),
    tfr_cycles = seq(2, 20, by = 0.5),
    tfr_mode = "percent",
    tfr_baseline = c(-0.45, -0.05),
    perm_contrasts = list(
      c("Pre-insight/Informed", "Pre-insight/Naive"),
      c("Insight/Informed", "Insight/Naive"),
      c("Post-insight/Informed", "Post-insight/Naive"),
      c("Insight/Informed", "Insight/Exclude_informed")
    ),
    tfr_components = list(
      name = list("alpha_beta"),
      tmin = list(0.6),
      tmax = list(1.2),
      fmin = list(8.0),
      fmax = list(20.0),
      roi = list(c("P3", "Pz", "P4", "PO3", "POz", "PO4"))
    ),
    perm_tmin = -0.4,
    perm_tmax = 1.4,
    n_jobs = 1
  )
}

@@

  # Fit the model for each ERP component
  map(deps, fit_mixed_models, formula = form, data = trials_control) %>%
    set_names(deps) -> models_control

  # Fit an additional model for event-related power, controlling for RTs
  form_rt <- ~ phase * condition + log(rt) +
    (phase * condition | participant_id) +
    (phase * condition | item_id)
  models_control$alpha_beta <-
    fit_mixed_models(form = form_rt, data = trials_main, dep = "alpha_beta")

@@

# Extract relevant statistics to print in the main text
map(models_control, function(mod) as_tibble(mod$contrasts)) %>%
  bind_rows(.id = "component") %>%
  rename(t_value = `t.ratio`, p_value = `p.value`) -> contrast_table_control
```

@@

Finally, we had wondered if the reduction in alpha/beta power might merely reflect differences in the timing of motor preparation between conditions, given the well-established link between motor processes and beta power over sensorimotor cortex [@kivalik2013].
To rule this out, we extracted single trial percent signal change based on the distribution of clusters from the permutation tests (time window 600–1,200 ms, frequency range 8–20 Hz, electrodes P3, Pz, P4, PO3, POz, and PO4; see Figures 3 and 4).
We then subjected these to a linear-mixed effects model that controlled for log-transformed reaction time as a covariate of no interest.
This confirmed the significant reduction in alpha/beta power for the semantically informed condition as compared to the naive condition in the insight phase, $b$ = `r filter(contrast_table_control, component == "alpha_beta" & phase == "Insight")$estimate`%, $t$(`r filter(contrast_table_control, component == "alpha_beta" & phase == "Insight")$df`) = `r filter(contrast_table_control, component == "alpha_beta" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "alpha_beta" & phase == "Insight")$p_value)`, as well as in the post-insight phase, $b$ = `r filter(contrast_table_control, component == "alpha_beta" & phase == "Post-insight")$estimate`%, $t$(`r filter(contrast_table_control, component == "alpha_beta" & phase == "Post-insight")$df`) = `r filter(contrast_table_control, component == "alpha_beta" & phase == "Post-insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "alpha_beta" & phase == "Post-insight")$p_value)`.

@@

```{r tabs1, results="asis"}
# Print table of materials
read_csv(here("example_stimuli", "stimuli.csv")) %>%
  mutate(
    match_ger = paste0(
      "\\textit{", match_noun_ger, "}, \\textit{", match_verb_ger, "}"
    ),
    match_en = paste0("{[", match_noun_en, ", ", match_verb_en, "]}"),
    nonmatch_ger = paste0(
      "\\textit{", nonmatch_noun_ger, "}, \\textit{", nonmatch_verb_ger, "}"
    ),
    nonmatch_en = paste0("{[", nonmatch_noun_en, ", ", nonmatch_verb_en, "]}"),
  ) %>%
  transmute(
    img = paste0(
      "\\includegraphics[valign=c,scale=0.25]{example_stimuli/", item, ".png}"
    ),
    match = paste(match_ger, match_en, sep = "\n") %>%
      kableExtra::linebreak(align = "l", linebreaker = "\n"),
    nonmatch = paste(nonmatch_ger, nonmatch_en, sep = "\n") %>%
      kableExtra::linebreak(align = "l", linebreaker = "\n")
  ) %>%
  apa_table(
    booktabs = TRUE,
    col.names = c(
      "Object", "Matching keywords", "Non-matching keywords"
    ),
    escape = FALSE,
    longtable = TRUE,
    caption = "Example stimuli\\smallskip",
    font_size = "footnotesize"
  )
```

@@

```{r, ress1a}
# Helper function for printing model summary, ANOVA (F tests), and contrasts
print_model_outputs <- function(model_object) {
  model <- model_object$model
  model@call$data <- NULL # Prevents cluttering the `summary` output
  print(summary(model))
  cat("\n")
  print(model_object$anova)
  cat("\nFollow-Up Contrasts (Simple Effects)\n")
  print(model_object$contrasts)
  cat("\n\n")
}

>>>>

  # Process EEG data
  res <- pipeline$group_pipeline(
    vhdr_files = vhdr_files,
    log_files = logs,
    output_dir = output_dir,
    epochs_dir = here(output_dir, "epochs"),
    report_dir = report_dir,
    downsample_sfreq = 125.0,
    bad_channels = NULL,
    ica_method = "fastica",
    ica_n_components = 0.99,
    highpass_freq = 0.1,
    lowpass_freq = 30.0,
    triggers = c(221, 222),
    epochs_tmin = -0.5,
    epochs_tmax = 1.5,
    baseline = c(-0.2, 0.0),
    reject_peak_to_peak = 150.0,
    components = list(
      "name" = list("P1", "N170", "N400"),
      "tmin" = list(0.1, 0.15, 0.4),
      "tmax" = list(0.15, 0.2, 0.7),
      "roi" = list(
        c("PO3", "PO4", "POz", "O1", "O2", "Oz"),
        c("P7", "P8", "PO7", "PO8", "PO9", "PO10"),
        c("C1", "C2", "Cz", "CP1", "CP2", "CPz")
      )
    ),
    average_by = c("phase/condition"),
    perform_tfr = TRUE,
    tfr_subtract_evoked = FALSE,
    tfr_freqs = seq(4, 40, by = 1.0),
    tfr_cycles = seq(2, 20, by = 0.5),
    tfr_mode = "percent",
    tfr_baseline = c(-0.45, -0.05),
    perm_contrasts = list(
      c("Pre-insight/Informed", "Pre-insight/Naive"),
      c("Insight/Informed", "Insight/Naive"),
      c("Post-insight/Informed", "Post-insight/Naive"),
      c("Insight/Informed", "Insight/Exclude_informed")
    ),
    perm_tmin = -0.4,
    perm_tmax = 1.4,
    n_jobs = 1
  )
}

@@

  # Fit the model for each component
  map(deps, fit_mixed_models, formula = form, data = trials_control) %>%
    set_names(deps) -> models_control

@@

# Extract relevant statistics to print in the main text
map(models_control, function(mod) as_tibble(mod$anova, rownames = "effect")) %>%
  bind_rows(.id = "component") %>%
  rename(f_value = `F value`, p_value = `Pr(>F)`) -> anova_table_control
map(models_control, function(mod) as_tibble(mod$contrasts)) %>%
  bind_rows(.id = "component") %>%
  rename(t_value = `t.ratio`, p_value = `p.value`) -> contrast_table_control
```

@@

Finally, we had wondered if the reduction in alpha/beta power might merely reflect differences in the timing of motor preparation between conditions, given the well-established link between motor processes and beta power over sensorimotor cortex [@kilavik2013].
To rule this out, we extracted single trial percent signal change based on the distribution of clusters from the permutation tests (time window 600–1,200 ms, frequency range 8–20 Hz, electrodes P3, Pz, P4, PO3, POz, and PO4; see Figures 3 and 4).
We then subjected these to a linear-mixed effects model that controlled for log-transformed reaction time as a covariate of no interest.
This confirmed the significant reduction in alpha/beta power for the semantically informed condition as compared to the naive condition in the insight phase, $b$ = `r filter(contrast_table_control, component == "alpha_beta" & phase == "Insight")$estimate`%, $t$(`r filter(contrast_table_control, component == "alpha_beta" & phase == "Insight")$df`) = `r filter(contrast_table_control, component == "alpha_beta" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "alpha_beta" & phase == "Insight")$p_value)`, as well as in the post-insight phase, $b$ = `r filter(contrast_table_control, component == "alpha_beta" & phase == "Post-insight")$estimate`%, $t$(`r filter(contrast_table_control, component == "alpha_beta" & phase == "Post-insight")$df`) = `r filter(contrast_table_control, component == "alpha_beta" & phase == "Post-insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "alpha_beta" & phase == "Post-insight")$p_value)`.

@@

```{r tabs1, results="asis"}
# Print table of materials
read_csv(here("example_stimuli", "stimuli.csv")) %>%
  mutate(
    match_ger = paste0(
      "\\textit{", match_noun_ger, "}, \\textit{", match_verb_ger, "}"
    ),
    match_en = paste0("{[", match_noun_en, ", ", match_verb_en, "]}"),
    nonmatch_ger = paste0(
      "\\textit{", nonmatch_noun_ger, "}, \\textit{", nonmatch_verb_ger, "}"
    ),
    nonmatch_en = paste0("{[", nonmatch_noun_en, ", ", nonmatch_verb_en, "]}"),
  ) %>%
  transmute(
    img = paste0(
      "\\includegraphics[valign=c,scale=0.25]{example_stimuli/",
      item_id,
      ".png}"
    ),
    match = paste(match_ger, match_en, sep = "\n") %>%
      kableExtra::linebreak(align = "l", linebreaker = "\n"),
    nonmatch = paste(nonmatch_ger, nonmatch_en, sep = "\n") %>%
      kableExtra::linebreak(align = "l", linebreaker = "\n")
  ) %>%
  apa_table(
    booktabs = TRUE,
    col.names = c(
      "Object", "Matching keywords", "Non-matching keywords"
    ),
    escape = FALSE,
    longtable = TRUE,
    caption = "Example stimuli\\smallskip",
    font_size = "footnotesize"
  )
```

@@

```{r, ress1a}
# Helper function for printing model summary, ANOVA (F tests), and contrasts
print_model_outputs <- function(model_object) {
  model_object$summary$data <- NULL # Prevents cluttering the summary output
  print(model_object$summary$data)
  cat("\n")
  print(model_object$anova)
  cat("\nFollow-Up Contrasts (Simple Effects)\n")
  print(model_object$contrasts)
  cat("\n\n")
}
